### 2022-07-01 about/vita.tex
New paper

\leftright{Citizen of Canada and Singapore}{3660 Rue Hutchison, Apt.\ 4}
\leftright{Email: marcel\_goh@yahoo.ca}{Montr\'eal, QC H2X 2H3, Canada}
\leftright{Webpage: marcelgoh.ca}{+1\thinspace\up(825\up)\thinspace 440-0681}

@@

\begingroup\frenchspacing
\papercount=3
\pubbegin P
\papitem (with Anna M. Brandenberger, Luc Devroye, and Rosie Y. Zhao)
Leaf multiplicity in a Bienaym\'e--Galton--Watson tree. {\sl Discrete Mathematics
and Theoretical Computer Science} {\bf 24},1 (2022), \#7, 16~pp. [arXiv:2105.12046]
\papitem (with Anna M. Brandenberger and Luc Devroye)
Root estimation in Galton--Watson trees. To appear in {\sl Random Structures and Algorithms}, 24~pp.
[arXiv:2007.05681]
\papitem (with Rosie Y. Zhao)
Arithmetic subsequences in a random ordering of an additive set.
{\sl Integers: Electronic Journal of Combinatorial Number Theory} {\bf 21} (2021), \#A89, 19~pp.
[arXiv:2012.12339]

@@

\begingroup\parindent=10pt
\thing (with Luc Devroye and Rosie Y. Zhao)
The independence number of a Bienaym\'e--Galton--Watson tree
and related parameters. {\sl arXiv preprint 2106.14389}, 20~pp.
\smallskip
\thing (with Jad Hamdan and Jonah Saks)
The lattice of arithmetic progressions. {\sl arXiv preprint 2106.05949}, 15~pp.
\endgroup
\endgroup%end the frenchspacing

>>>>

\leftright{Citizen of Canada and Singapore}{2-9602 74th Avenue NW}
\leftright{Email: marcel\_goh@yahoo.ca}{Edmonton, AB T6E 1E6}
\leftright{Webpage: marcelgoh.ca}{+1\thinspace\up(825\up)\thinspace 440-0681}

@@

\begingroup\frenchspacing
\papercount=4
\pubbegin P
\papitem (with Luc Devroye and Rosie Y. Zhao)
On the peel number and the leaf-height of a Galton--Watson tree.
To appear in {\sl Combinatorics, Probability and Computing}, 20~pp. [arXiv:2106.14389]
\papitem (with Anna M. Brandenberger, Luc Devroye, and Rosie Y. Zhao)
Leaf multiplicity in a Bienaym\'e--Galton--Watson tree. {\sl Discrete Mathematics
and Theoretical Computer Science} {\bf 24},1 (2022), \#7, 16~pp. [arXiv:2105.12046]
\papitem (with Anna M. Brandenberger and Luc Devroye)
Root estimation in Galton--Watson trees. To appear in {\sl Random Structures and Algorithms}, 24~pp.
[arXiv:2007.05681]
\papitem (with Rosie Y. Zhao)
Arithmetic subsequences in a random ordering of an additive set.
{\sl Integers: Electronic Journal of Combinatorial Number Theory} {\bf 21} (2021), \#A89, 19~pp.
[arXiv:2012.12339]

@@

\begingroup\parindent=10pt
\thing (with Jonah Saks)
Alternating-sum statistics for certain sets of integers. {\sl arXiv:2206.12535} (2022), 12~pp.
\smallskip
\thing (with Jad Hamdan and Jonah Saks)
The lattice of arithmetic progressions. {\sl arXiv preprint 2106.05949} (2021), 15~pp.
\endgroup
\endgroup%end the frenchspacing

### 2022-07-01 about/vita_professional.tex
New paper

\leftright{+1\thinspace\up(825\up)\thinspace 440-0681}{3660 Rue Hutchison, Apt.\ 4}
\leftright{Email: marcel\_goh@yahoo.ca}{Montr\'eal, QC H2X 2H3, Canada}
\leftright{Webpage: marcelgoh.ca}{}

@@

@@

\sectheader{Research Interests}

@@

\begingroup\parindent=10pt
\thing (with Jad Hamdan and Jonah Saks)
The lattice of arithmetic progressions. {\sl arXiv preprint 2106.05949}, 15~pp.
\endgroup
\endgroup%end the frenchspacing

\leftright{\bf Tlingit verb parsing}{\bf February -- April 2021}
\smallskip
A rule-based program that finds regularity in Tlingit verbs, written in Python.

\leftright{\bf Sorting algorithms on manifolds}{\bf May -- August 2020}
\smallskip
Research project under the supervision of Michael Lipnowski.
Studied algorithms that investigate the topology of group actions on locally symmetric spaces.
Work involved writing of code in OCaml and PostScript that generates illustrations of certain quotient
spaces, in various models of hyperbolic geometry.

\leftright{\bf Bytecode compiler and interpreter}{\bf February -- June 2019}
\smallskip
Under the supervision of Adam Dingle, wrote a bytecode compiler and virtual machine for a subset of Python.
OPythn includes support for lists, dictionaries, named and anonymous functions, objects, and classes.
It is implemented in OCaml using Ocamllex for lexing and Menhir for parsing.

\leftright{\bf Alonzo $\lambda$-calculus interpreter}{\bf May -- June 2019}
\smallskip
Wrote an interpreter for the untyped $\lambda$-calculus that performs $\alpha$-conversion
and $\beta$-reduction. Includes an interactive environment that allows users to bind names to
terms. Implemented in Haskell.

\leftright{\bf Escape-time fractals}{\bf May 2019}
\smallskip
Made an interactive graphical program to generate and explore fractals. Implemented using the SDL2
graphics library and written in \CEE. (HackPrague 2019)

\leftright{\bf Nim}{\bf January 2019}
\smallskip
Implemented the game of Nim graphically using Processing. Worked on game logic and created the soundtrack
using an $8$-bit sequencer. (ConUHacks IV)

\leftright{\bf CourseTalk}{\bf November 2018}
\smallskip
Created a web chat app using Node.js and React.js. (HackPrinceton Fall 2018)

>>>>

\leftright{+1\thinspace\up(825\up)\thinspace 440-0681}{2-9602 74 Avenue NW, Apt.\ 4}
\leftright{Email: marcel\_goh@yahoo.ca}{Edmonton, AB T6E 1E6}
\leftright{Webpage: marcelgoh.ca}{Canada}

@@

\leftright{\bf Tlingit verb parsing}{}
\smallskip
A rule-based program that finds regularity in Tlingit verbs, written in Python.

\leftright{\bf Sorting algorithms on manifolds}{}
\smallskip
Research project under the supervision of Michael Lipnowski.
Studied algorithms that investigate the topology of group actions on locally symmetric spaces.
Work involved writing of code in OCaml and PostScript that generates illustrations of certain quotient
spaces, in various models of hyperbolic geometry.

\leftright{\bf Bytecode compiler and interpreter}{}
\smallskip
Under the supervision of Adam Dingle, wrote a bytecode compiler and virtual machine for a subset of Python.
OPythn includes support for lists, dictionaries, named and anonymous functions, objects, and classes.
It is implemented in OCaml using Ocamllex for lexing and Menhir for parsing.

\leftright{\bf Alonzo $\lambda$-calculus interpreter}{}
\smallskip
Wrote an interpreter for the untyped $\lambda$-calculus that performs $\alpha$-conversion
and $\beta$-reduction. Includes an interactive environment that allows users to bind names to
terms. Implemented in Haskell.

\leftright{\bf Escape-time fractals}{}
\smallskip
Made an interactive graphical program to generate and explore fractals. Implemented using the SDL2
graphics library and written in \CEE. (HackPrague 2019)

\leftright{\bf Nim}{}
\smallskip
Implemented the game of Nim graphically using Processing. Worked on game logic and created the soundtrack
using an $8$-bit sequencer. (ConUHacks IV)

\leftright{\bf CourseTalk}{}
\smallskip
Created a web chat app using Node.js and React.js. (HackPrinceton Fall 2018)

\begingroup\parindent=10pt
\thing (with Jonah Saks)
Alternating-sum statistics for certain sets of integers. {\sl arXiv:2206.12535} (2022), 12~pp.
\smallskip
\thing (with Jad Hamdan and Jonah Saks)
The lattice of arithmetic progressions. {\sl arXiv:2106.05949} (2021), 15~pp.
\endgroup
\endgroup%end the frenchspacing

@@

\goodbreak
\sectheader{Research Interests}

@@
